---
title: "Assignment pml predict"
author: "P Sohan"
date: "10/20/2020"
output: html_document
---


## Brief Backgd

We are Performing this project to predict the way with which participants perform a barbell lift. Now a days we have the technology like Fitbit, Nike fuelband to collect data about a persons activities.
The data used here is from: http://groupware.les.inf.puc-rio.br/har

## Intials

We use various training and test sets from the sources online.

```{r DLding, message = FALSE}
library(caret)
#usingcaret
setwd("C:/Users/MAHE/Documents")
#setingpath
#gtnurls
exeURL <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
#gtnurlss
exetURL <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
#trngtransfer
trining <- read.csv(url(exeURL))
#tstng_trnfr
tstingg <- read.csv(url(exetURL))
label<- createDataPartition(trining$classe, p = 0.7, list = FALSE)
trinbb <- trining[label, ]
tstbbb <- trining[-label, ]
```


There are a lot of variables in the data set so we try to reduce them with the help of the below given chunk.
Alot of these variables are not needed so we just get rid of them.
The main goal of this stage is to reduce the data set by gettinig rid of some unwanted datas.


```{r DClng}
NnZro <- nearZeroVar(trinbb)
#varzero
trinbb <- trinbb[ ,-NnZro]
#trnngset
tstbbb <- tstbbb[ ,-NnZro]
#label_usntr
label<- apply(trinbb, 2, function(x) mean(is.na(x))) > 0.95
#bhbhb
trinbb <- trinbb[, -which(label, label== FALSE)]
tstbbb <- tstbbb[, -which(label, label == FALSE)]
trinbb <- trinbb[ , -(1:5)]
tstbbb <- tstbbb[ , -(1:5)]
```



## plotinggph

We have removed uncessary variabls. Now we will see how the vsr depend on each other. For that matter we create plot and observe.We use the corrplot library. We then create a relationship plot among the variables.


```{r CrelPlot, fig.width=12, fig.height=8}
library(corrplot)
#lib_remember
corrMat <- cor(trinbb[,-54])
#placing_it
corrplot(corrMat, method = "color", type = "upper", tl.cex = 0.8, tl.col = rgb(0,0,0))
```
Dark regions have high relnsp tg[ns]


## first modell Dcsntree

Now after the initiol steps we use three methodss for modelling th sets we have. We would try to find out which one among these methods would yeild us the most accurate results . We will be having plots at the end of every model in order to find out which of the plot is the best representation ptim.


### Dsdnt

```{r DnTree, message = FALSE, warning = FALSE, fig.width=18, fig.height=10}
library(rpart)
library(rpart.plot)
library(rattle)
#libs
set.seed(13908)
#sdng
modelldD <- rpart(classe ~ ., data = trinbb, method = "class")
#modelled
fancyRpartPlot(modelldD)
#usgn_fn
predicttdD <- predict(modelldD, tstbbb, type = "class")
#prdtng
confMattrrrD <- confusionMatrix(predicttdD, tstbbb$classe)
confMattrrrD
```

### secong modell of randFrt



```{r RrFost, message = FALSE}
#we are going to try using randomforest
library(caret)
#libs
set.seed(13908)
#putng_ctrl
control <- trainControl(method = "cv", number = 3, verboseIter=FALSE)
#putng_modelled
modellrrR <- train(classe ~ ., data = trinbb, method = "rf", trControl = control)
modellrrR$finalModel
#prdictd_val
predictteddR <- predict(modellrrR, tstbbb)
confMatrRrrf <- confusionMatrix(predictteddR, tstbbb$classe)
confMatrRrrf
```

### third modell of gbm



```{r GBMplottng, message = FALSE}
#trying gbm method
library(caret)
#libcaret
set.seed(13908)
#cntrl_put
control <- trainControl(method = "repeatedcv", number = 5, repeats = 1, verboseIter = FALSE)
#modelled
modelGBbbm <- train(classe ~ ., data = trinbb, trControl = control, method = "gbm", verbose = FALSE)
modelGBbbm$finalModel
#prditd_usgn
predictGBbbm <- predict(modelGBbbm, tstbbb)
confMatrGBbbm <- confusionMatrix(predictGBbbm, tstbbb$classe)
confMatrGBbbm
```

the most accurate result is obtained from Random forest method. So we will use this method to get results for the tests.

## Getting Results

```{r resultprd, messages = FALSE}
#finding out prediction for the set
predictteddR <- predict(modellrrR, tstingg)
predictteddR
```

